---
title: "Week1_RMarkdown"
author: "Ivan Lima"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### A bulleted list with sub-bullets under at least one item

* A bulleted list
  + A sub-bullet 1
  + A sub-bullet 2

### A numbered list

1. A numbered list 1
2. A numberd list 2

### Some words italicized

*My italicized word*

### Some words in bold print 
**My bold word**

### Two levels of headers

# My first level of header

## My second level of header

### My third level of header

### The results of some R code without showing the code

```{r echo=FALSE}
my_number_hidden_code <- "The code is hidden but the result is not"
```
`r my_number_hidden_code`

# My table of text at least 3 columns wide and 3 rows long

Table Header 1 | Table Header2 | Table header 3
------------- | ------------- | --------------
Content Cell 1.1  | Content Cell 2.1  | Content Cell 3.1
Content Cell 1.2  | Content Cell 2.2  | Content Cell 3.2
Content Cell 1.3  | Content Cell 2.3  | Content Cell 3.3

### A plot (show the code that generates the plot)

```{r echo=FALSE}
x <- sample(0:10, 10)
y <- 3 * x
plot(x, y)
```

### Your session info (as output from R)

```{r echo=FALSE}
print(sessionInfo())
```





